The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-06-19 razzo-abstract.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{abstract}

  % From 'How to construct a Nature summary paragraph'

@@

  % One sentence summarising the main
  % result (with the words “here we show”
  % their equivalent).
  Here we show the error we make in our inference,
  when nature has varying degrees of co-occuring speciation.

@@

  % Two or three sentences to provide a
  % broader perspective, readily comprehensible
  % to a scientist in any discipline, may be included
  % in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced
  % by their inclusion. Under these circumstances, the length of the paragraph can be up to 300 words.
  % (The above example is 190 words without the final section, and 250 words with it).

\end{abstract}

{\bf Keywords:} computational biology, evolution, phylogenetics, Bayesian analysis, tree prior
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography % MEE style

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{abstract}
% From 'How to construct a Nature summary paragraph'

@@

% One sentence summarising the main
% result (with the words “here we show”
% their equivalent).
Here we show the error we make in our inference,
when nature has varying degrees of co-occurring speciation.

@@

% Two or three sentences to provide a
% broader perspective, readily comprehensible
% to a scientist in any discipline, may be included
% in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced
% by their inclusion. Under these circumstances, the length of the paragraph can be up to 300 words.
\end{abstract}
{\bf Keywords:} computational biology, evolution, phylogenetics, Bayesian analysis, tree prior

### 2019-06-19 razzo-results.tex

\section{Results}
\begin{itemize}

\item We expected the effect of $s$ on $e$ to be monotonously increasing
function (figure \ref{fig:h_1}). Figure \ref{fig:1} shows the effect 
measured in this experiment.

\input{razzo-fig_1.tex}

\item We expected the effect of the number of taxa on the relation
between $s$ and $e$ to be neutral (figure \ref{fig:h_5}). 
Figure \ref{fig:5} shows the effect 
measured in this experiment.

\input{razzo-fig_5.tex}

\item We expected the effect of the number of taxa on the variance
of $e$ for similar values of $s$ to decrease (figure \ref{fig:h_6}). 
Figure \ref{fig:6} shows the effect 
measured in this experiment.

\input{razzo-fig_6.tex}

\item We expected the effect of extinction on the relation
between $s$ and $e$ to be neutral (figure \ref{fig:h_2}). 
Figure \ref{fig:2} shows the effect 
measured in this experiment.

\input{razzo-fig_2.tex}

\item

\end{itemize}

>>>>

\section{Results}
Here we present the results as show in Fig.~\ref{fig:results}...

\input{razzo-figures/fig_results.tex}
